RSA + Scalar implicature / TBD

### 2015-11-28 models/RSA+AmbiguousSemantics.Rmd
exploring scale entropy measures

---
title: "RSA + Scalar implicature / TBD"
author: "BPeloquin/MFrank"
date: "October 29, 2015"
output:
  html_document:
    highlight: pygments
    theme: flatly
    toc: yes
    toc_depth: 2
---
```{r load_data, results="hide", message=FALSE, warning=FALSE}
rm(list = ls())
setwd("/Users/benpeloquin/Desktop/Projects/scalar_implicature/models")
source("../analysis/useful_dplyr.R")
library(rjson)
library(ggplot2)
library(MASS)
library(jsonlite)
library(tidyr)
```

@@

d <- d1 %>% 
  gather(base, alt, 
         palatable, liked, good, loved, some, all, 
         delicious, excellent, memorable, unforgettable) %>%
  mutate(base = as.character(base)) %>%
  rowwise %>%
  mutate(scale = ifelse(base == "some" | base == "all", "some_all", 
                        ifelse(base == "palatable" | base == "delicious", "palatable_delicious",
                               ifelse(base == "liked" | base == "loved", "liked_loved",
                                      ifelse(base == "good" | base == "excellent", 
                                             "good_excellent", "memorable_unforgettable"))))) %>%
  group_by(scale, alt) %>%
  summarise(n = n())

@@

>>>>

---
title: "RSA + Scalar implicature / TBD"
author: "BPeloquin/MFrank"
date: "October 29, 2015"
output:
  html_document:
    highlight: pygments
    theme: flatly
    toc: yes
    toc_depth: 2
---
```{r load_data, results="hide", message=FALSE, warning=FALSE}
rm(list = ls())
setwd("/Users/benpeloquin/Desktop/Projects/scalar_implicature/models")
library(tidyr)
source("../analysis/useful_dplyr.R")
library(dplyr)
library(rjson)
library(ggplot2)
library(MASS)
library(jsonlite)

@@

d = d1 %>% 
  gather(base, alt, 
         palatable, liked, good, loved, some, all, 
         delicious, excellent, memorable, unforgettable) %>%
  mutate(base = as.character(base)) %>%
  rowwise %>%
  mutate(scale = ifelse(base == "some" | base == "all", "some_all", 
                        ifelse(base == "palatable" | base == "delicious", "palatable_delicious",
                               ifelse(base == "liked" | base == "loved", "liked_loved",
                                      ifelse(base == "good" | base == "excellent", 
                                             "good_excellent", "memorable_unforgettable"))))) %>%
  group_by(scale, alt) %>%
  summarise(n = n())

@@

```{r}

pers = d[d$scale == "good_excellent", ]$n / sum(d[d$scale == "good_excellent", ]$n)
H.ge = -sum(pers * log2(pers))
pers = d[d$scale == "liked_loved", ]$n / sum(d[d$scale == "liked_loved", ]$n)
H.ll = -sum(pers * log2(pers))
pers = d[d$scale == "memorable_unforgettable", ]$n / sum(d[d$scale == "memorable_unforgettable", ]$n)
H.mu = -sum(pers * log2(pers))
pers = d[d$scale == "some_all", ]$n / sum(d[d$scale == "some_all", ]$n)
H.sa = -sum(pers * log2(pers))
pers = d[d$scale == "palatable_delicious", ]$n / sum(d[d$scale == "palatable_delicious", ]$n)
H.pd = -sum(pers * log2(pers))

H.ge
H.ll
H.mu
H.sa
H.pd
